### 2025-07-09 paper/sections/other/main_results.qmd
final table

using CTExperiments
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.Plots
using CTExperiments.StatsBase
using Random

@@

df = final_table(res_dir)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
formatters = (
    PrettyTables.ft_round(1,findall(.!contains.(names(df),"Acc"))),
    PrettyTables.ft_round(2,findall(contains.(names(df),"Acc")))
)
for fname in ["paper/quarto_aaai/tables/main.tex","paper/preprint/tables/main.tex"]
    tabulate_results(
        inputs; 
        table_type=:tabular, 
        save_name=fname, 
        wrap_table=false, 
        alignment=[:l,fill(:r,size(df,2)-1)...],
        formatters=formatters
    )
end
```

>>>>

using CTExperiments
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.Plots
using CTExperiments.StatsBase
using Random
using Serialization

@@

df_mtbl = aggregate_ce_evaluation(
    mtbl_dir; 
    ratio=true, 
    rebase=false, 
    y="distance", 
    agg_further_vars=["run", "lambda_energy_eval"], 
    total_uncertainty=false, 
    drop_models=["linear"]
)
df = final_table(res_dir; tbl_mtbl=df_mtbl)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
formatters = (
    PrettyTables.ft_round(1,findall(.!contains.(names(df),"Acc"))),
    PrettyTables.ft_round(2,findall(contains.(names(df),"Acc")))
)
for fname in ["paper/quarto_aaai/tables/main.tex","paper/preprint/tables/main.tex"]
    tabulate_results(
        inputs; 
        table_type=:tabular, 
        save_name=fname, 
        wrap_table=false, 
        alignment=[:l,fill(:r,size(df,2)-1)...],
        formatters=formatters
    )
end
```
